### 2015-05-08 evaluation.tex
update in evaluation

As an example of the second case, we discovered the following race in the generic\_nvram char driver: during the \texttt{llseek} entry point, the driver is accessing the file offset \texttt{file->f\_pos} without first acquiring a lock (\texttt{file} is passed as a parameter to \texttt{llseek}). This can lead to a race if the driver invokes \texttt{llseek} from another thread passing the same \texttt{file} object as a parameter. When we investigated another char driver that uses the same APIs, we saw that it was protecting the offset access in its \texttt{llseek} entry point with a mutex. This made us suspicious that the race we found in generic\_nvram could be real. We filed a bug report, but did not manage to get a response yet.

>>>>

As an example of the second case, we found the following race in the generic\_nvram char driver (see Example~\ref{fig:data_race_example} for the source code): during the \texttt{llseek} entry point, the driver is accessing the file offset \texttt{file->f\_pos} without first acquiring a lock (\texttt{file} is passed as a parameter to \texttt{llseek}). This can lead to a race if the driver invokes \texttt{llseek} from another thread passing the same \texttt{file} object as a parameter. When we investigated another char driver that uses the same APIs, we saw that it was protecting the offset access in its \texttt{llseek} entry point with a mutex. This made us suspicious that the race we found in generic\_nvram could be real. We filed a bug report, but did not manage to get a response yet.
